\maketitle

\begin{abstract}
    I need to add an abstract here. I think it will include things about the pervasive need across multiple disciplines to understand and quantify the functions of AIs. I will try to talk about different research areas and outline each of their needs and some of the methods that they currently  use. I hope to be able to identify several places for opportunity, and possibly introduce some fields to others.
\end{abstract}

\section{Introduction}
    Trying to outline the objectives and goals of this paper. A `Short' treatment of trust and its definitions. Address the definition that we are interested (human-autonomy interaction). Discuss different fields that are interested in trust. Review mechanisms that are used in each field. Propose introspection as the set of all of the used methods, plus those that are missing.
    
    Introduces the idea of trust (and references some of the work in this area). This paper introduces a topic called \emph{circumspection of artificial agents}, which is defined as agents that produce the tools to be circumspective. Or in other words they possess the tools to be \emph{introspective} and \emph{extrospective}. Highlights how circumspective tools are necessary for human-agent trust relationships. It highlights the work that has already been done in many other research fields, which is knows by other names and descriptions, and shows that they all have common themes.

    This section needs to be used to explain the problem, and why it is interesting, in more detail. I need to cite papers \cite{Back1996-jp,Ernest2016}

    Some ideas for content:

    \begin{itemize}
        \item Introduce trust, with a bias towards non-interhuman trust (i.e. human-computer, human-robot, human-machine)
        \item introduce, define circumspective agents.
        \item List some of the fields that are interested in circumspection (even if they don't know it yet), give examples of why
        \item Break down the interests from other fields into a subset of shared goals
        \item others\ldots
    \end{itemize}

\section{The Case for Human-Agent Trust}
    Add stuff in here about trust, different kinds, different definitions.

    \begin{itemize}
        \item xAI
        \item LIME
        \item 
    \end{itemize}

    Trying out several citations. So and So \cite{Wang2016} said this. but \cite{Thompson1933} said something else. Hopefully \cite{Doyle2014} agrees with that, but it doesn't seem like \cite{Gelbart2015} does. I really liked reading \cite{Snoek2015}.

\section{Different key points}
    \subsection{exemplar}
    \subsection{model based}
    \subsection{etc\ldots}

\section{Conclusion}
    Revisit the key ideas of the paper:

    \begin{itemize}
        \item trust is a key factor for human-agent interaction
        \item many fields care about it
        \item circumspection is a common framework
        \item circumspection has several key properties that encompass the different research fields
    \end{itemize}

\newpage
